A general framework for learning planning action models

### 2018-06-12 doc/aij18/motivation.tex
minor changes

The main novelty of \FAMA with respect to other approaches lies in that our system is capable of handling \PO and \NO action sequences, which combined with \PO and \NO state trajectories, make the learning task more challenging. This essentially brings one key difference: the transition between two given observed states may now involve more than one action; i.e., $\theta(s_i,\tup{a_1,\ldots,a_k})=s_{i+1}$, with $k \leq 1$, $k$ unknown and unbound, and so the horizon of the input plan traces is no longer known now.

@@

Regarding the metric to evaluate the learned action models, we can observe in Table \ref{table:models_comparison2} that most of the approaches use a similar metric that consists of (1) counting the missing and extra fluents that appear in the learned model wrt the GTM and (2), normalizing this error by the the total number of all the possible preconditions and effects of an action model. This is an \emph{optimistic} metric since error rates are not normalized by the size of the actual GTM model. Hence, because the set of preconditions and effects of the GTM model is usually smaller than the set of all possible preconditions and effects, it turns out the metric may output error rates just slightly below 100\% for totally wrong learned models.

In order to overcome this limitation, we propose to use two standard metrics from ML, {\em precision} and {\em recall}. These two metrics are frequently used in {\em pattern recognition}, {\em information retrieval} and {\em binary classification} and are more informative that simply counting the number of errors in the learned model or computing the {\em symmetric difference} between the learned and the reference model~\cite{davis2006relationship}.

>>>>

The main novelty of \FAMA with respect to other approaches lies in that our system is capable of handling \PO and \NO action sequences, which combined with \PO and \NO state trajectories, make the learning task more challenging. This essentially brings one key difference: the transition between two given observed states may now involve more than one action; i.e., $\theta(s_i,\tup{a_1,\ldots,a_k})=s_{i+1}$, with $k \geq 1$, $k$ unknown and unbound, and so the horizon of the input plan traces is no longer known now.

@@

Regarding the metric to evaluate the learned action models, we can observe in Table \ref{table:models_comparison2} that most of the approaches use a similar metric that consists in (1) counting the missing and extra fluents that appear in the learned model wrt the GTM and (2), normalizing this error by the the total number of all the possible preconditions and effects of an action model. This is an \emph{optimistic} metric since error rates are not normalized by the size of the actual GTM model. Hence, because the set of preconditions and effects of the GTM model is usually smaller than the set of all possible preconditions and effects, it turns out the metric may output error rates below 100\% for totally wrong learned models.

In order to overcome this limitation, we propose to use two standard metrics from ML, {\em precision} and {\em recall}. These two metrics are frequently used in pattern recognition, information retrieval and binary classification and are more informative that simply counting the number of errors in the learned model or computing the {\em symmetric difference} between the learned and the reference model~\cite{davis2006relationship}.
